DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-02 paper/overview.tex
tbd
Change images for platform and track
Add evaluation subsection for benchmark tests
Also add log for training a model on Raspberry Pi 3 that took over 4
hours to finish.

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{Picar_Picture}
  \caption{DeepPicar platform.}
  \label{fig:overview}
\end{figure}

@@

% data collection and training.
To collect the training data, a human pilot manually drives the RC car
on a small track we created (Figure~\ref{fig:track}) to record
timestamped video and contol commands. The stored data is then copied 
to a desktop computer, which equips a NVIDIA GTX 1060 GPU, where we
train the network to accerate training speed. 
For comparison, training the network on the Raspbeery Pi 3 takes
approximately 6 hours, whereas it takes only about 5 minutes on the
desktop computer using the GTX 1060 GPU.

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{figs/track}
  \caption{A track for training/testing.\fixme{replace this}}
  \label{fig:track}
\end{figure}

@@

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{figs/DeepPicar_platform}
  \caption{DeepPicar platform.}
  \label{fig:overview}
\end{figure}

@@

% data collection and training.
To collect the training data, a human pilot manually drives the RC car
on a small track we created (Figure~\ref{fig:track}) to record
timestamped video and contol commands. The stored data is then copied 
to a desktop computer, which equips a NVIDIA GTX 1060 GPU, where we
train the network to accerate training speed. 
For comparison, training the network on the Raspbeery Pi 3 takes
approximately 4 hours, whereas it takes only about 5 minutes on the
desktop computer using the GTX 1060 GPU.

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth, angle=270]{figs/track_new}
  \caption{A track for training/testing.\fixme{replace this}}
  \label{fig:track}
\end{figure}

@@

\fixme{Discuss the limitation of the RC car platform: discrete
  control, web camera latency}
